Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-03-11 ms.tex
caption

\begin{figure*}
\includegraphics[width=\textwidth]{miller.pdf}
\caption{\label{fig:miller} $\epsilon_X \Mdot c^2/L_{\rm edd}$ predicted
  from our models compared to $L_X/L_{\rm edd}$ values (red stars) and
  upper limits (red triangles) from \citet{Miller+15}.
  $\epsilon_X=10^{-4}$ in the left-hand panel and $\epsilon_X=0.1
  \frac{\Mdot}{0.01 \MdotEdd}$ in the right-hand panel. The green and
  blue curves represent our predictions for core ($\Gamma=0.1$)
  and cusp ($\Gamma=0.8$) galaxies respectively. They are calculated
  from equation~\eqref{eq:mdot_analytic}, with the wind heating
  parameter, $v_w$ and mass return parameter, $\eta$, corresponding to
  the the average star formation histories in
  \citet{MosterNaab+:2013a} (the black lines in
  Figures~\ref{fig:vwSources}--see
  Appendix~\ref{app:windheat} for a detailed description).
  We also show upper limits $\epsilon_X \Mdot c^2/L_{\rm edd}$ from
  thermal stability (purple) and Ia supernovae (orange).}
\end{figure*}

>>>>

\begin{figure*}
\includegraphics[width=\textwidth]{miller.pdf}
\caption{\label{fig:miller} Average (unresolved) nuclear X-ray luminosity $\langle L_X \rangle = \epsilon_X \Mdot c^2$ as a function of SMBH mass, predicted from our models for the average star formation history (Fig.~\ref{fig:bh_growth}; {\it black line}) calculated for the average Nuker power-law index $\Gamma(M_{\bullet})$ derived from the galaxy sample of \citet{LauerFaber+:2007a}.  Shown for comparison are the measurements $L_X/L_{\rm edd}$ values (red stars) and
  upper limits (red triangles) from the \citet{Miller+15} sample of early-type galaxies, with a green line showing the best power-law fit $\langle L_X/L_{\rm edd}\rangle \propto M_{\bullet}^{\alpha}$, with $\alpha = -0.2$.  The left panel shows the case of a constant radiative efficiency $\epsilon_X=10^{-4}$, while the right hand panel shows an efficiency $\epsilon_X=
  \left(\frac{\epsilon_{\rm bol}}{0.1}\right)\frac{\Mdot}{\MdotEdd}$ predicted by some models for radiatively inefficient accretion.  Also shown for comparison are the X-ray luminosities calculated using the maximum thermally-stable accretion rate ({\it orange line}), SN Ia-regulated accretion rate, and Compton-regulated accretion rate ({\it pink line}),  again calculated for the average star formation history.}
\end{figure*}
